\subsection{Functional Requirements}
\textbf{Sign-up e Login}
\begin{itemize}
    \item \textbf{R1:} The platform allows the Cyclists to create an account.
    \item \textbf{R2:} The platform allows Cyclists to authenticate.
    \item \textbf{R3:} The platform allows the access as a Guest. 
    \item \textbf{R4:} The platform allows Cyclists to view their personal account.
    \item \textbf{R5:} The platform allows Cyclists to modify their personal account.
\end{itemize}
\textbf{Route Creation and Publication}
\begin{itemize}
    \item \textbf{R6:} The platform allows the Cyclists to create a new route through a manual creation process.
    \item \textbf{R7:} The platform allows the Cyclists to create a new route through an automatic creation process.
    \item \textbf{R8:} The platform allows the Cyclists to confirm and complete the automatically acquired information.
    \item \textbf{R9:} The platform collects data from the device sensors.
    \item \textbf{R10:} The platform collects weather data and enriches the path's statistics.
    \item \textbf{R11:} The platform allows the Cyclists to evaluate the status of a route. 
    \item \textbf{R12:} The platform allows the Cyclists to publish/unpublish a route.
    \item \textbf{R13:} The platform allows the Cyclists to delete a route.
\end{itemize}
\textbf{Route Visualization}
\begin{itemize}
    \item \textbf{R14:} The platform allows the Cyclists to visualize a list of paths in the personal inventory with the possibility to filter them.
    \item \textbf{R15:} The platform allows the User to view the details of a path such as the map, the statistics and the status.
    \item \textbf{R16:} The platform allows the User to visualize the details of the routes related to a path.
\end{itemize}
\textbf{Route Search and Navigation}
\begin{itemize}
    \item \textbf{R17:} The platform allows the User to search a path by setting the start and the end points with a kilometer tolerance.
    \item \textbf{R18:} The platform suggests to the User a list of available routes ranked by score.
    \item \textbf{R19:} The platform supports path navigation by allowing users to follow routes that have been previously created.
\end{itemize}
\textbf{Scoring, Merging and Ranking}
\begin{itemize}
    \item \textbf{R20:} The platform merges the status when more than one is present.
    \item \textbf{R21:} The platform computes a score for each path based on path's status and average speed.
\end{itemize}
\newpage
\subsection{Requirements Traceability Matrix}
\begin{table}[h]
\centering
\small
\setlength{\tabcolsep}{1pt}        % riduce lo spazio orizzontale tra colonne
\renewcommand{\arraystretch}{1.4} % riduce lo spazio verticale tra righe
\begin{tabular}{|>{\centering\arraybackslash}m{1cm}|*{14}{>{\centering\arraybackslash}p{1cm}|}}

\hline
   & \rotatebox{90}{Authentication service}
   & \rotatebox{90}{Account service}
   & \rotatebox{90}{Inventory service}
   & \rotatebox{90}{ManagePath service}
   & \rotatebox{90}{ManageRoute service}
   & \rotatebox{90}{Navigation system}
   & \rotatebox{90}{Recommendation system}
   & \rotatebox{90}{ManageSensorsData service }
   & \rotatebox{90}{Weather conditions}
   & \rotatebox{90}{SensorData}
   & \rotatebox{90}{API Gateway}
   & \rotatebox{90}{DBMSs}
   & \rotatebox{90}{User Interface} \\ 
\hline
R1  & X & & & & & & & & & & X & X & X \\ \hline
R2  & X & & & & & & & & & & X & X & X \\ \hline
R3  & X & & & & & & & & & & X & X & X \\ \hline
R4  & & X & & & & & & & & & X & X & X \\ \hline
R5  & & X & & & & & & & & & X & X & X \\ \hline
R6  & & & & X & X & & & & & & X & X & X \\ \hline
R7  & & & & & X & & & X & & X & X & X & X \\ \hline
R8  & & & & X & X & & & & & & X & X & X \\ \hline
R9  & & & & & & & & X & & X & X & X & \\ \hline
R10 & & & & & & & & & X & & X & X & \\ \hline
R11 & & & & & X & & & & & & X & X & X \\ \hline
R12 & & & & X & X & & X & & & & X & X & X \\ \hline
R13 & & & & X & X & & X & & & & X & X & X \\ \hline
R14 & & & X & & & & & & & & X & X & X \\ \hline
R15 & & & & X & X & & & & & & X & X & X \\ \hline
R16 & & & & X & X & & & & & & X & X & X \\ \hline
R17 & & & & & & & X & & & & X & X & X \\ \hline
R18 & & & & & & & X & & & & X & X & X \\ \hline
R19 & & & & & & X & & X & & X & X & X & X \\ \hline
R20 & & & & & & & X & & & & X & X & \\ \hline
R21 & & & & & & & X & & & & X & X & \\ \hline
\end{tabular}
\caption{Requirements Traceability Matrix}
\label{tab:rtm}
\end{table}




